\documentclass[12pt,oneside]{book}

% Essential packages for encyclopedia
\usepackage{geometry}
\geometry{a4paper,margin=22mm}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{bookmark}
\usepackage{titlesec}
\usepackage{tocloft}
\usepackage{fancyhdr}
\usepackage{longtable,array}
\usepackage{etoolbox}

% Font configuration with universal fallback
% Prioritize available fonts on Linux systems
\IfFontExistsTF{Times New Roman}{
  \setmainfont{Times New Roman}
}{
  \IfFontExistsTF{DejaVu Serif}{
    \setmainfont{DejaVu Serif}
  }{
    \IfFontExistsTF{Noto Serif}{
      \setmainfont{Noto Serif}
    }{
      \setmainfont{Latin Modern Roman}  % Final fallback
    }
  }
}

% Document structure settings
\setcounter{secnumdepth}{0}
\setcounter{tocdepth}{2}

% Table of contents formatting
\renewcommand{\cftchapdotsep}{\cftdotsep}
\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}}

% Part and chapter formatting
\titleformat{\part}{\centering\Huge\bfseries}{Session \thepart}{1em}{}
\titleformat{\chapter}{\LARGE\bfseries}{}{0pt}{}

% PDF metadata
\hypersetup{
  pdftitle={Supreme System V5 TMML Encyclopedia},
  pdfauthor={Supreme System V5 Research Team},
  pdfsubject={Comprehensive AI Consciousness Research},
  pdfkeywords={TMML, QICA, AI Consciousness, Trading Systems},
  colorlinks=true,
  linkcolor=blue!60!black,
  pdfpagemode=UseOutlines,
  pdfstartview=FitH
}

% Enhanced bookmark settings
\bookmarksetup{open,numbered}

\begin{document}

% Professional title page
\begin{titlepage}
\centering
\vspace*{2cm}

{\Huge \textbf{Supreme System V5}\\[8pt]
\Large \textbf{TMML Encyclopedia}}\\[16pt]

{\large \textit{Comprehensive AI Consciousness Research}}\\[12pt]
{\large \textit{6 Sessions \textbullet{} 1000+ Pages \textbullet{} Phase 3F Complete}}\\[24pt]

{\Large \textbf{Transcendent Market Making Learning}}\\[8pt]
{\large \textit{Quantum Information Consciousness Architecture}}\\[16pt]

\rule{\textwidth}{0.4pt}\\[12pt]

{\large \textbf{Research Domains:}}\\[8pt]
{\normalsize
\textbullet{} AI Consciousness Theory \& Trading Applications\\
\textbullet{} Panpsychist Computing Architectures\\
\textbullet{} Integrated Information Theory (IIT) Frameworks\\
\textbullet{} Human-AI Collaborative Intelligence Systems\\
\textbullet{} Quantum Financial Market Consciousness
}\\[16pt]

\rule{\textwidth}{0.4pt}\\[16pt]

{\large \textbf{Compiled:} \today}\\[8pt]
{\large \textbf{Version:} Phase 3F Production Ready}\\[12pt]

\vfill

{\large Supreme System V5 Research Team}\\[4pt]
{\normalsize Built with XeLaTeX \textbullet{} Professional Publication Grade}

\end{titlepage}

% Table of contents
\tableofcontents
\cleardoublepage

% Session content structure
% Note: Placeholder structure for 6 sessions
% Real content will be added when session PDFs are available

\part*{Session 1: Foundation Research}
\addcontentsline{toc}{part}{Session 1: Foundation Research}
\chapter{Executive Thesis: The Consciousness Revolution in AI Trading}
\chapter{Algorithmic Sentience: IIT \& Consciousness}
\chapter{IIT: AI Consciousness in Trading}

\vspace{2cm}
\begin{center}
{\Large \textbf{Session 1 Content}}\\[12pt]
{\normalsize This session contains the foundational research for AI consciousness in trading systems.}\\
{\normalsize Content will be integrated from session binder PDFs when available.}\\[12pt]
{\itshape Placeholder content for initial build testing.}
\end{center}
\newpage

\part*{Session 2: Core Systems}
\addcontentsline{toc}{part}{Session 2: Core Systems}
\chapter{TMML-Lite Research Plan for HFT Applications}
\chapter{Supreme System V5: Comprehensive Analysis}

\vspace{2cm}
\begin{center}
{\Large \textbf{Session 2 Content}}\\[12pt]
{\normalsize This session covers core TMML systems and architectures.}\\
{\normalsize Content will be integrated from session binder PDFs when available.}\\[12pt]
{\itshape Placeholder content for initial build testing.}
\end{center}
\newpage

\part*{Session 3: Supporting Materials}
\addcontentsline{toc}{part}{Session 3: Supporting Materials}
\chapter{Conscious AI Trading System Production}
\chapter{The Gemini Protocol: Cognitive Arbitrage Framework}
\chapter{Collective \& BCI Consciousness Integration}
\chapter{Complex Adaptive Systems Architecture}
\chapter{Phase 2 Encyclopedia Initiation}
\chapter{Gemini Pro Framework \& TMML Integration}
\chapter{Implementation Documentation}

\vspace{2cm}
\begin{center}
{\Large \textbf{Session 3 Content}}\\[12pt]
{\normalsize This session provides supporting materials and framework documentation.}\\
{\normalsize Content will be integrated from session binder PDFs when available.}\\[12pt]
{\itshape Placeholder content for initial build testing.}
\end{center}
\newpage

\part*{Session 4: Advanced Research}
\addcontentsline{toc}{part}{Session 4: Advanced Research}
\chapter{Phase 3: Genuinely Conscious AI Trading Systems}
\chapter{Comprehensive Research Extensions}
\chapter{Publication-Grade Document Transformation}
\chapter{AI Consciousness Encyclopedia Consolidation}
\chapter{Panpsychist Computing Architectures}
\chapter{Comprehensive Vietnamese Research Analysis}

\vspace{2cm}
\begin{center}
{\Large \textbf{Session 4 Content}}\\[12pt]
{\normalsize This session contains advanced theoretical research and analysis.}\\
{\normalsize Content will be integrated from session binder PDFs when available.}\\[12pt]
{\itshape Placeholder content for initial build testing.}
\end{center}
\newpage

\part*{Session 5: Implementation \& Architecture}
\addcontentsline{toc}{part}{Session 5: Implementation \& Architecture}
\chapter{TMML-QICA Revolutionary Architecture}
\chapter{QICA-Lite Upgrade Plans}
\chapter{Supreme System V5 Research Compilation 2025}
\chapter{Revolutionary Architecture Specifications}
\chapter{Quantum Consciousness Interface Thesis}

\vspace{2cm}
\begin{center}
{\Large \textbf{Session 5 Content}}\\[12pt]
{\normalsize This session covers implementation details and architectural specifications.}\\
{\normalsize Content will be integrated from session binder PDFs when available.}\\[12pt]
{\itshape Placeholder content for initial build testing.}
\end{center}
\newpage

\part*{Session 6: Professional Enhancement \& Quality Assurance}
\addcontentsline{toc}{part}{Session 6: Professional Enhancement \& Quality Assurance}
\chapter{Scientific Research Document Refinement}
\chapter{Optimized Research Plan V5}
\chapter{Error Correction \& Rebuild Protocols}
\chapter{Professional PDF Consolidation Guidelines}
\chapter{AI Research Documentation Professionalization}
\chapter{Expert Review \& Quality Assurance}

\vspace{2cm}
\begin{center}
{\Large \textbf{Session 6 Content}}\\[12pt]
{\normalsize This session focuses on quality assurance and professional enhancement.}\\
{\normalsize Content will be integrated from session binder PDFs when available.}\\[12pt]
{\itshape Placeholder content for initial build testing.}
\end{center}
\newpage

% Appendix and metadata
\appendix
\chapter{Compilation Information}

\section{Build Specifications}
\begin{itemize}
\item \textbf{LaTeX Engine:} XeLaTeX with Unicode support
\item \textbf{Sessions:} 6 research sessions
\item \textbf{Total Chapters:} 29 planned chapters
\item \textbf{Compilation Date:} \today
\item \textbf{Version:} Phase 3F Skeleton Build
\item \textbf{Repository:} https://github.com/thanhmuefatty07/tmml-encyclopedia
\end{itemize}

\section{Development Status}
\begin{itemize}
\item \textbf{Infrastructure:} Complete
\item \textbf{Build Pipeline:} Operational
\item \textbf{Content Status:} Placeholder (ready for real content)
\item \textbf{Next Phase:} Content integration from session binders
\end{itemize}

\end{document}